\textsc{Rils}-\textsc{Rols} : Robust Symbolic Regression via Iterated Local Search and Ordinary Least Squares

### 2022-11-10 paper_resources/doc/paper.tex
polish

\begin{figure}[!ht]
	\centering
	\begin{subfigure}[b]{0.40\textwidth}
		\includegraphics[  width=290pt,height=180pt]{plots/Feynman__strogatz_noise_0_0.pdf}
		\caption{No noise}
		\label{fig:CDplots-no-noise}
	\end{subfigure}

@@

	\begin{subfigure}[b]{0.40\textwidth}
		\includegraphics[  width=290pt,height=180pt]{plots/Feynman__strogatz_noise_0_01.pdf}
		\caption{Level of noise equal to 0.01.}
		\label{fig:CDplots-noise0.01}
	\end{subfigure}
	\caption{CD plots comparisons in terms of exact percentages over all problem instances from the both ground-truth benchmark sets,  varying levels of noise.}
	\label{fig:cd-plots-exact-pcts}
\end{figure}

>>>>

\begin{figure}[!ht]
	\centering
	\begin{subfigure}[b]{0.40\textwidth}
		\includegraphics[  width=320pt,height=180pt]{plots/Feynman__strogatz_noise_0_0.pdf}
		\caption{No noise}
		\label{fig:CDplots-no-noise}
	\end{subfigure}

@@

	\begin{subfigure}[b]{0.40\textwidth}
		\includegraphics[  width=290pt,height=180pt]{plots/Feynman__strogatz_noise_0_01.pdf}
		\caption{Level of noise equal to 0.01.\fxnote{polish labels}}
		\label{fig:CDplots-noise0.01}
	\end{subfigure}
	\caption{CD plots comparisons in terms of exact percentages over all problem instances from the both ground-truth benchmark sets,  varying levels of noise. \fxnote{Polish labels}}
	\label{fig:cd-plots-exact-pcts}
\end{figure}
